Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law

### 2023-12-06 manuscript/manuscript.qmd
lol use already-existing province lookup table

```{r calc-summaries}
provinces <- ongo_mapdata |> 
  st_drop_geometry() |> 
  mutate(rank = dense_rank(-ro_count)) |> 
  mutate(list_name = janitor::make_clean_names(province_en_short)) |> 
  split(~ list_name)

>>>>

```{r calc-summaries}
provinces <- ongo_mapdata |> 
  drop_na(province_code) |> 
  st_drop_geometry() |> 
  mutate(rank = dense_rank(-ro_count)) |> 
  mutate(list_name = janitor::make_clean_names(province_en)) |> 
  split(~ list_name)
